Meta RL analyses

### 2019-03-13 meta_RL_analyses.Rmd
Plots for commitee meeting

result_subdirs = c(# "nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   #"language", "language_simplified",
                   "language_noncompositional", "language_simplified", "language_meta_nontoggling",
                   "language_noncompositional_old", "language_simplified_random_holdout")

name_run_type = function(run_type) { # names for plotting
  case_when(run_type == "basic" ~ "Targeted 10% holdout",
            run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
            run_type == "language_noncompositional_old" ~ "Old language (targeted 10%)",
            run_type == "language_simplified" ~ "Old language (targeted 10%)",
            run_type == "language_simplified_random_holdout" ~ "Language (random 50%)",
            T ~ run_type)
}

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type == "basic"),
             "game_type", "reward", "is_new_game",
             optimal_baselines,
             most_correlated_baselines %>%
               filter(run_type == "basic",
                      is_new_game == "Held out")) 
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3)
```

@@

#ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
```

```{r}
avg_reward_d %>% filter(is_new_game)
```

```{r}
ggplot(avg_reward_d %>% filter(is_new_game, run_type %in% c("basic", "nometa")), aes(x=run_type, fill=run_type, y=avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge", width=0.5) +
  scale_fill_brewer(palette="Set1")
```

@@

```{r}
ggplot(avg_sweep_d %>%
         filter(run_type == "basic"), aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_wrap(~ game_type)

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "nometa")), aes(x=size, color=named_run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
language_d = load_d(results_dir, c("language_noncompositional_old", 
                                   #"language",  "language_nontoggling_random_holdout", 
                                   "language_simplified", "language_meta_nontoggling", "language_noncompositional",
                                   "language_simplified_random_holdout"), num_runs, "new_language_rewards")

language_d = language_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = check_if_new_game(run_type, game_str))
```

@@

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             optimal_baselines) +
  facet_wrap(. ~ named_run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("writing/figures/language_basic.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
```

@@

```{r}
lang_meta_d = load_d(results_dir, c(
                              # "language", "language_simplified", "language_meta_nontoggling", "language_nontoggling_random_holdout", 
                               "language_noncompositional_old", "language_simplified", "language_simplified_random_holdout",
                               "language_meta_nontoggling", "language_noncompositional"
                               ), num_runs, "new_language_meta_true_losses")

@@

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 #ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
```
# embeddings

>>>>

result_subdirs = c(# "nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer") # "basic_only_one", "basic_only_one_ho")

language_result_subdirs = c(                  
  "meta_batch_64", "meta_batch_128", "meta_batch_256",
  #"language", "language_simplified",
  "language_noncompositional", "language_simplified", # "language_meta_nontoggling",
  "language_noncompositional_old", "language_simplified_random_holdout",
  "language_mb_128_ne_15","language_mb_128_ne_20")

joint_result_subdirs = c("joint_lnex_mb_256_ne_20",
                         "joint_lnex_mb_256_ne_10",
                         "joint_lnex_mb_256_ne_5",
                         "joint_lnex_lw_mb_256_ne_10",
                         "joint_lnex_lw_mb_128_ne_10",
                         "joint_lnex_lw_mb_128_ne_5")

result_subdirs = c(result_subdirs, language_result_subdirs, joint_result_subdirs)

name_run_type = function(run_type) { # names for plotting
  case_when(run_type == "basic" ~ "Targeted 10% holdout",
            run_type == "basic_random_holdout_longer" ~ "Random 50% holdout",
            run_type == "language_noncompositional_old" ~ "Old language (targeted 10%)",
            run_type == "language_simplified" ~ "Old language (targeted 10%)",
            run_type == "meta_batch_128" ~ "Language (targeted 10%)",
            run_type == "language_simplified_random_holdout" ~ "Language (random 50%)",
            T ~ run_type)
}

@@

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type == "basic"),
             "game_type", "reward", "is_new_game",
             optimal_baselines,
             most_correlated_baselines %>%
               filter(run_type == "basic",
                      is_new_game == "Held out")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
```

```{r}
summary_plot(reward_d %>%
               filter(epoch == 0,
                      run_type == "basic_random_holdout_longer"),
             "game_type", "reward", "is_new_game",
             optimal_baselines,
             most_correlated_baselines %>%
               filter(run_type == "basic_random_holdout_longer",
                      is_new_game == "Held out")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic.png", width=5, height=3)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/basic_random_holdout_half.png", width=5, height=3.5)
```

@@

#ggsave("writing/figures/basic_meta_learning.png", width=5, height=3.5)
```

```{r}
#avg_reward_d %>% filter(is_new_game)
```

```{r}
# ggplot(avg_reward_d %>% filter(is_new_game, run_type %in% c("basic", "nometa")), aes(x=run_type, fill=run_type, y=avg_reward)) +
#   geom_bar(stat="identity", position="dodge") +
#   geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge", width=0.5) +
#   scale_fill_brewer(palette="Set1")
```

@@

```{r}
ggplot(avg_sweep_d %>%
         filter(run_type %in% c("basic", "meta_batch_256", "joint_lnex_lw_mb_256_ne_10", "joint_lnex_lw_mb_128_ne_10")), aes(x=size, color=is_new_game, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set2") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ run_type)

@@

```{r}
ggplot(avg_sweep_d %>% filter(run_type %in% c("basic", "meta_batch_256", "meta_batch_128", "meta_batch_64", "language_mb_128_ne_15", "joint_lnex_mb_256_ne_5", "joint_lnex_mb_256_ne_10"),
                              size < 200), aes(x=size, color=named_run_type, y=avg_reward)) +
  geom_point() +
  geom_line() +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi)) +
  scale_color_brewer(palette="Set1") +
  xlab("Meta Set Size") +
  facet_grid(game_type ~ is_new_game)
```

@@

```{r}
language_d = load_d(results_dir, c(language_result_subdirs, joint_result_subdirs), num_runs, "new_language_rewards")

language_d = language_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = check_if_new_game(run_type, game_str),
         is_new_game = factor(is_new_game, labels=c("Trained", "Held out")))
```

@@

```{r}
summary_plot(language_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             optimal_baselines) +
  facet_wrap(. ~ named_run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("writing/figures/language_basic.png", width=5, height=3.5)
#ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/crappy_language.png", width=5, height=3)
```

```{r}
summary_plot(language_d %>%
               filter(epoch == 0,
                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
             "game_type", "reward", "is_new_game",
             optimal_baselines,
             most_correlated_baselines %>%
               filter(run_type %in% c("meta_batch_128", "language_simplified_random_holdout"),
                      is_new_game == "Held out")) +
  facet_wrap(. ~ named_run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("writing/figures/language_basic.png", width=7, height=3.5)
ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_basic.png", width=7, height=3.5)
```
# joint language + examples

```{r}
joint_d = load_d(results_dir, joint_result_subdirs, num_runs, "new_joint_lnex_rewards")

joint_d = joint_d %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one | is_only_one_ho)) %>%
  gather(game_str, reward, starts_with("game")) %>%
  mutate(game_type = str_extract(game_str, "high_card|match|straight_flush|pairs_and_high|sum_under"),
         losers = grepl("l_1", game_str),
         black_valuable = grepl("bv_1", game_str),
         suits_rule = grepl("sr_1", game_str),
         is_new_game = check_if_new_game(run_type, game_str))
```

```{r}
ggplot(joint_d %>%
         filter(epoch == 0,
                is_new_game),
       aes(x=run, y=reward, fill=as.factor(run))) +
  geom_hline(yintercept=0.,
             linetype=2,
             alpha=0.5) +
  geom_violin(position="dodge") +
  geom_point(aes(group=as.factor(run)),
             size=3,
             stat="summary", fun.y="mean",
             position=position_dodge(width=0.9)) +
  scale_color_brewer(palette="Set2") + 
  ylim(-0.6, 0.6) +
  labs(x="Run",
       y="Reward density on held-out tasks") + 
  guides(fill=guide_legend(title="Run")) +
  facet_wrap(~named_run_type)
```

```{r}
summary_plot(joint_d %>%
               filter(epoch == 0),
             "game_type", "reward", "is_new_game",
             optimal_baselines) +
  facet_wrap(. ~ named_run_type) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("writing/figures/joint_lnex.png", width=5, height=3.5)
```

@@

```{r}
lang_meta_d = load_d(results_dir, c(language_result_subdirs, joint_result_subdirs), num_runs, "new_language_meta_true_losses")

@@

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
 #ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
```

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0,
                      run_type %in% c("meta_batch_128", "language_simplified_random_holdout")),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave("~/Documents/grad/res/psych/ARRR/figures/meta_RL/language_meta.png", width=7, height=3.5)
#ggsave("writing/figures/meta_mapping.png", width=5, height=3.5)
```

# embeddings
